
## The Gap Procedure: For the identification of phylogenetic clusters in HIV-1 sequence data

The Gap Procedure is a distance-based clustering algorithm that can be used for finding distinct groups of genetically similar DNA sequences. In the literature involving HIV, clusters are typically ascertained on the basis of high clade support values on a phylogenetic tree. The Gap Procedure bypasses the need for estimating phylogenetic trees thereby dramatically decreasing computational burden. As demonstrated in the quick example below, the only input required by this algorithm is an aligned set of DNA sequences: 

```{r}
library(ape)
library(GapProcedure)
data(simulation)
(x <- as.DNAbin(as.alignment(as.matrix(simulation[,-1]))))
GP <- GapProcedure(x)
GP$classification
```

Windows users will have to download the zip file [here](http://www.math.mcgill.ca/ivrbik/software.html) and type the following command in R
```{r}
  install.packages("path/to/file/GapProcedure_0.0.0.9000.zip",repos=NULL,type="source")
```


If using a Linux or Mac, this package can be downloaded directly from github using the devltools package:
```{r, eval=FALSE}
library(devtools)
devtools::install_github("vrbiki/GapProcedure")
```



This package is maintained by [Irene Vrbik](http://www.math.mcgill.ca/ivrbik/).  For an online version of the vignette [Click here](http://www.math.mcgill.ca/ivrbik/vignette.html).  Please report any issues [here](https://github.com/vrbiki/GapProcedure/issues).

